NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models: Supplemental Materials

### 2018-03-31 paper/application.tex
integration grammar fix
grammar fix

\section{Application Scenarios}
\label{sec:caseStudy}
% \shusen{A full case study that driven by the visualization task and the question associated with them}
%In this section, we discuss application scenarios, in which the domain experts utilize the
To better illustrate how the proposed perturbation-driven exploration tool helps researchers interpret the neural network model, we present five application scenarios gathered by the domain experts who integrated the proposed tool in their analysis workflow.

@@

% perturb input, attention
\begin{figure*}[t]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{pipelineUpdate}
  \vspace{-6mm}
 \caption{
Experiment with all configurations for the label reassignment optimization. As shown in (d), the update of attention stage seems to have significantly less impact on the prediction result compared to the classifier or encoder of the model.
 }
  \vspace{-4mm}
\label{fig:pipelineUpdate}
\end{figure*}

@@

%
%However, to understand how the model should
\begin{figure*}[t]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{depTreeExample}
  \vspace{-6mm}
 \caption{
Dependency tree provides valuable information that can help fix the prediction error.
In (a), the model mistakenly aligns the word green, which lead to wrong prediction.  
After examining the dependency tree (highlighted by pink squares), we can see the two \textbf{green} are attached to different words.
In (b), by editing the attention and forcing the two \textbf{green}'s alignment to be zero, the prediction label is corrected to \emph{neutral}. 
 }
\label{fig:depTreeExample}
 \vspace{-4mm}
\end{figure*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scenario 5: Handcraft Example Exploration}
To test the limits of the model, domain experts often handcraft ``extreme'' examples (as such the Facebook IPO example discussed in Section~\ref{sec:languageInference}) that they know most models will have a difficult time making correct inference.
%
The researchers start with a set of experiments they plan to run, from which, they will develop new hypotheses for further analysis.
%
In some way, we can think of such a process as a natural blend of all previously discussed scenarios. However, instead of with specific goal in mind, the domain experts focus on probing around to uncover any interesting or out-of-ordinary behaviors in the model.
%

>>>>

\section{Application Scenarios}
\label{sec:caseStudy}
% \shusen{A full case study that driven by the visualization task and the question associated with them}
%In this section, we discuss application scenarios, in which the domain experts utilize the
To better illustrate how the proposed perturbation-driven exploration tool helps researchers interpret the neural network model, we present five application scenarios gathered by the domain experts who integrated the proposed tool into their analysis workflow.

@@

% perturb input, attention
\begin{figure*}[t]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{pipelineUpdate}
  \vspace{-6mm}
 \caption{
Experiment with all configurations for the label reassignment optimization. As shown in (d), the update of the attention stage seems to have significantly less impact on the prediction result compared to the classifier or encoder of the model.
 }
  \vspace{-4mm}
\label{fig:pipelineUpdate}
\end{figure*}

@@

%
%However, to understand how the model should
\begin{figure*}[t]
\centering
\vspace{-2mm}
 \includegraphics[width=1.0\linewidth]{depTreeExample}
  \vspace{-6mm}
 \caption{
The dependency tree provides valuable information that can help fix the prediction error.
In (a), the model mistakenly aligns the word green, which leads to an incorrect prediction.  
After examining the dependency tree (highlighted by pink squares), we can see the two \textbf{greens} are attached to different words.
In (b), by editing the attention and forcing the alignment of the two \textbf{greens} to be zero, the prediction label is corrected to \emph{neutral}. 
 }
\label{fig:depTreeExample}
 \vspace{-4mm}
\end{figure*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Scenario 5: Handcraft Example Exploration}
To test the limits of the model, domain experts often handcraft ``extreme'' examples (such as the Facebook IPO example discussed in Section~\ref{sec:languageInference}) for which they know most models will have difficulty making a correct inference.
%
The researchers start with a set of experiments they plan to run, from which they will develop new hypotheses for further analysis.
%
In some way, we can think of such a process as a natural blend of all previously discussed scenarios. However, instead of having a specific goal in mind, the domain experts focus on probing around to uncover any interesting or out-of-the-ordinary behaviors in the model.
%

### 2018-03-31 paper/implementation.tex
grammar fix

\subsection{Implementation}
\label{sec:implementation}
The initial learning curve and workflow setup cost of the tool are often the most significant barriers for user adaptation.
In the proposed system, we approach these challenges by designing the system as a python library rather than as a monolithic standalone application. 
Just like a python plotting library, the different pieces of the visualization can be accessed individually, which help ease the initial learning curve. 
The individual components can also be combined in any configuration desired by the user via a simple Python API to better fit into one's workflow.
More importantly, the library based design allows easily integrate with existing model implemented in python.
%
To create a visualization, users only need to import the library, create an instance of the visualization object, and specify a set of callback functions, such as generating a prediction, accessing attention, to link the visualization to their NLP models (see the code example in \textbf{Appendix B}).

>>>>

\subsection{Implementation}
\label{sec:implementation}
The initial learning curve and workflow setup cost of the tool are often the most significant barriers for user adaptation.
In the proposed system, we approach these challenges by designing the system as a Python library rather than as a monolithic standalone application. 
Just like a Python plotting library, the different pieces of the visualization can be accessed individually, which helps ease the initial learning curve. 
The individual components can also be combined in any configuration desired by users via a simple Python API to better fit into one's workflow.
More importantly, the library-based design allows easy integration with the existing model implemented in Python.
%
To create a visualization, users only need to import the library, create an instance of the visualization object, and specify a set of callback functions, such as generating a prediction, accessing attention, to link the visualization to their NLP models (see the code example in \textbf{Appendix B}).
